Detecting Stylistic Variation in Pop Production

### 2023-12-01 outputs/paper/paper.qmd
yassified it

We find that, in both models, `danceability` is the strongest predictor of whether a song has been produced by Antonoff. Additionally, when we look at how danceability relates to other features in the dataset, we find that the differences in these relationships are informative: the degree to which danceability's relationships with other features vary helps us most accurately determine if Antonoff produced a song. In other words, using danceability along with its interactions with other dataset features gives us the most accurate predictions.

@@

lr_data %>%
  select(-producer, -tempo, -loudness, -mode) %>%
  pivot_longer(cols = -is_antonoff, names_to = "feature", values_to = "value") %>%
  ggplot(aes(x = feature, y = value, fill = factor(is_antonoff))) +
  geom_boxplot(alpha = 0.6, position = position_dodge(width = 0.8)) +
  scale_fill_manual(values = c("blue", "orange"), labels = c("No", "Yes")) +
  theme_minimal() +
  labs(fill = "Antonoff", x = "Feature", y = "Value") + 
  coord_flip()

@@

antonoff_vip |>
  group_by(Sign) |>
  slice_max(Importance, n = 15) |>
  ungroup() |>
  ggplot(aes(Importance, fct_reorder(Variable, Importance), fill = Sign)) +
  geom_col() +
  facet_wrap(vars(Sign), scales = "free_y") +
  labs(y = NULL) +
  theme(legend.position = "none") +
  theme_minimal()
```

@@

@@

ggplot(df_importance_long, aes(x = reorder(variable, importance), y = importance)) +
  geom_bar(stat = "identity", fill = "pink") +  
  facet_wrap(~producer, scales = "fixed") + 
  coord_flip() +
  labs( 
       x = "Variable", 
       y = "Mean Decrease Gini") +
  theme_minimal()

@@

ggplot(selected_data, aes(x=term, y=danceability, fill=producer)) +
  geom_bar(stat="identity", position="dodge") +
  labs(y="Danceability Score", x= "Feature") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

>>>>

We find that, in both models, `danceability` is the strongest predictor of whether a song has been produced by Antonoff, and the strongest predictor in differentiating between producers generally. Additionally, when we look at how danceability relates to other features in the dataset, we find that the differences in these relationships are informative: the degree to which danceability's relationships with other features vary helps us most accurately classify tracks. In other words, using danceability along with its interactions with other dataset features gives us the most accurate predictions.

@@

lr_data %>%
  select(-producer, -tempo, -loudness, -mode) %>%
  pivot_longer(cols = -is_antonoff, names_to = "feature", values_to = "value") %>%
  ggplot(aes(x = feature, y = value, fill = factor(is_antonoff))) +
  geom_boxplot(alpha = 0.6, position = position_dodge(width = 0.8)) +
  scale_fill_manual(values = c("#B0C4DE", "#9ACD32"), labels = c("No", "Yes")) +
  theme_minimal() +
  labs(fill = "Antonoff", x = "Feature", y = "Value") + 
  coord_flip()

@@

antonoff_vip |>
  group_by(Sign) |>
  slice_max(Importance, n = 15) |>
  ungroup() |>
  ggplot(aes(Importance, fct_reorder(Variable, Importance), fill = Sign)) +
  geom_col() +
  facet_wrap(vars(Sign), scales = "free_y") +
  labs(y = NULL) +
  theme(legend.position = "none") +
  theme_minimal() +
  scale_fill_manual(values = c(
    "#FAD4A6", 
    "#A4D4AE"))

@@

vibrant_colors <- c(
  "#FAD4A6", # Peach Puff: A light, peachy tone
  "#D3AE8C", # Tan: A muted, earthy tan color
  "#B0C4DE", # Light Steel Blue: A soft, pastel blue
  "#F1BAC3", # Light Pink: A pale pink shade
  "#D1E0E0", # Powder Blue: A light, airy grey-blue
  "#E7BE88", # Burlywood: A warm, beige color
  "#C8A680", # Pale Goldenrod: A deeper, more saturated tan
  "#A4D4AE", # Pale Green: A light, refreshing green
  "#E2B0B0", # Rosy Brown: A soft coral tone
  "#9ACD32"  # Yellow Green: A bright, springy green
)

@@

ggplot(df_importance_long, aes(x = reorder(variable, importance), y = importance, fill = variable)) +
  geom_bar(stat = "identity") +  
  facet_wrap(~producer, scales = "fixed") + 
  coord_flip() +
  labs(x = "Variable", y = "Mean Decrease Gini") +
  theme_minimal() +
  scale_fill_manual(values = vibrant_colors)

@@

ggplot(selected_data, aes(x=term, y=danceability, fill=producer)) +
  geom_bar(stat="identity", position="dodge") +
  labs(y="Danceability Score", x= "Feature") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = c(
    "#9ACD32", #springy green
    "#E7BE88", # Rich warm beige
    "#A4D4AE", # Pale green
    "#D3AE8C", # Vibrant taupe
    "#B0C4DE", # Lively soft blue
    "#F1BAC3", # Vivid blush pink
    "#D1E0E0", # Bright light gray
    "#B0C4DE", # Vivid sky blue
    "#A4D4AE" # Pale green
  ))
```
